Adopting agile in the large: motivations, success factors and challenges

### 2014-01-07 journal/article.tex
Organizing research method

@@

@@

@@

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. The selection
of primary studies was done as a keyword based database search and manual
filtering of included studies. The filtering process was executed independently
by two researchers (Dikert, Paasivaara), and the process was audited by a third
external researcher (Lassenius).

We deviated from Kitchenham's guideline in the parts of study assessment and
data extraction. These deviations are explained below.
--> This is maybe not true! The study assessment can also be done qualitatively.

\subsection{Inclusion criteria}
- pitää olla systemaattinen
- pitää olla toistettava
==> Perustuu enimmäkseen siihen että on 2 tutkijaa toistamassa

@@

A key question in the study was the definition of \emph{large scale}.
--> Needs to have complexity in software design?? --> What is complexity in software?
    Is ``complexity'' an issue in agile?
    What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
--> Some people see cost as a definition for large scale, some see code base
    size [Petersen], some see project duration [Bjarnson?]. These are all
    related, but do not relate to any specific problem. You can spend X amount
    of money, but it does not in itself make any difference if the money is
    spent in an agile way.
--> Formal definitions (EU, etc.) look at project costs or company turnover.
    These definitions do not take a standpoint on complexity of the product, so
    they do not matter in the context of SDMs.

@@

\subsection{Coding and synthesis}

An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. The coding was also designed to have a contextual
part and a findings part as suggested by Cruzes and Dybå \cite{Cruzes2011a}. A
list of codes was established for contextual information, as presented in Table
\ref{table:contextualcodes}. Codes related to the research questions were chosen
to be created by an inductive process. The reason for inducting codes rather
than using an a priori approach was to avoid the researchers' previous
assumptions of the research area to affect the choice of codes. To give
direction for code induction seven different code families were established (see
Table \ref{table:codefamilies}). A description defining scope and examples for
codes were defined for each family. The example codes would not necessarily be
used as actual codes, and would not represent the entire or final scope of the
families.

@@

The total accumulated codes and quotes of the integrated deductive and inductive
coding process are presented in Table \ref{table:codecount}. The total number of
quotations is less than the sum of quotations in the categories because a single
quotation may have multiple codes.

@@

Inter-rater statistics

                    Maria
           excl   ???   incl    TOT
     excl  1578    18    15    1611
Kimi ???     84    17     8     109
     incl    51    42    62     155
     TOT   1713    77    85    1875

???'s =  169
in/ex = 1706

Pr(Kimi, in) = in / (tot)  =  155 / 1857 = 0.0619
Pr(Kimi, ex) = ex / (tot)  = 1611 / 1857 = 0.8675
Pr(Maria, in) = in / (tot) =   85 / 1857 = 0.0458
Pr(Maria, ex) = ex / (tot) = 1713 / 1857 = 0.9225

Pr(e) = Pr(Kimi, in) * Pr(Maria, in) + Pr(Kimi, ex) * Pr(Maria, ex) = 0.8031

Pr(a) = (ex-ex + in-in) / tot = 0.8831

k = 0.4063

\subsection{Validation of coding}

Before proceeding with the synthesis we conducted an experiment with the goal to
reveal the objectiveness of the coding by examining the amount of difference the
codings of two independent researchers may have. In the experiment Dikert and
Paasivaara coded independently a sample of five primary documents. The sample
was hand picked to present a representative subset of the source material. The
coding was done relying only on the above guidelines, and the researchers were
careful not to discuss the choice of codes or interpretations relating to codes
before the experiment was completed. Finally the independent codings of the two
researchers were analyzed with two metrics: by the number of matching themes
found, and by the amount of overlap in quotations similar codes have.

>>>>

The goal of the research was to aggregate evidence on how large organizations
transform into an agile way of working. The research was conducted as a
systematic litterature review, based on empirical studies.

@@

The following research questions were set to guide the research process.

@@

\subsection{Definition of large scale}

A key question in the study was the definition of \emph{large scale}. Large
scale requires additional coordination and makes communication difficult
compared to software development in small teams.

--> Needs to have complexity in software design?? --> What is complexity in software?
    Is ``complexity'' an issue in agile?
    What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
--> Some people see cost as a definition for large scale, some see code base
    size [Petersen], some see project duration [Bjarnson?]. These are all
    related, but do not relate to any specific problem. You can spend X amount
    of money, but it does not in itself make any difference if the money is
    spent in an agile way.
--> Formal definitions (EU, etc.) look at project costs or company turnover.
    These definitions do not take a standpoint on complexity of the product, so
    they do not matter in the context of SDMs.

@@

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. The selection
of primary studies was done as a keyword based database search and manual
filtering of included studies. The filtering process was executed independently
by two researchers (Dikert, Paasivaara). The selected primary studies were coded
for data extraction and analysis. The entire process was audited by a third
external researcher (Lassenius).

We deviated from Kitchenham's guideline on the part of data extraction. Instead
of using data extraction forms we analyzed the primary studies by coding.

\subsubsection{Inclusion criteria}

- pitää olla systemaattinen
- pitää olla toistettava
==> Perustuu enimmäkseen siihen että on 2 tutkijaa toistamassa

@@

\subsubsection{Study selection}

@@

\subsubsection{Coding of primary documents}

The primary documents were coded using the Atlas TI qualitative data analysis software.
An integrated deductive and inductive approach was chosen for coding the primary
studies \cite{Cruzes2011a}. The coding was also designed to have a contextual
part and a findings part as suggested by Cruzes and Dybå \cite{Cruzes2011a}. A
list of codes was established for contextual information, as presented in Table
\ref{table:contextualcodes}. Codes related to the research questions were chosen
to be created by an inductive process. The reason for inducting codes rather
than using an a priori approach was to avoid the researchers' previous
assumptions of the research area to affect the choice of codes. To give
direction for code induction seven different code families were established (see
Table \ref{table:codefamilies}). A description defining scope and examples for
codes were defined for each family. The example codes would not necessarily be
used as actual codes, and would not represent the entire or final scope of the
families.

@@

The total accumulated codes and quotations of the integrated deductive and
inductive coding process are presented in Table \ref{table:codecount}. The total
number of quotations is less than the sum of quotations in the categories
because a single quotation may have multiple codes.

@@

% Inter-rater statistics
%
%                     Maria
%            excl   ???   incl    TOT
%      excl  1578    18    15    1611
% Kimi ???     84    17     8     109
%      incl    51    42    62     155
%      TOT   1713    77    85    1875
%
% ???'s =  169
% in/ex = 1706
%
% Pr(Kimi, in) = in / (tot)  =  155 / 1857 = 0.0619
% Pr(Kimi, ex) = ex / (tot)  = 1611 / 1857 = 0.8675
% Pr(Maria, in) = in / (tot) =   85 / 1857 = 0.0458
% Pr(Maria, ex) = ex / (tot) = 1713 / 1857 = 0.9225
%
% Pr(e) = Pr(Kimi, in) * Pr(Maria, in) + Pr(Kimi, ex) * Pr(Maria, ex) = 0.8031
%
% Pr(a) = (ex-ex + in-in) / tot = 0.8831
%
% k = 0.4063

\subsubsection{Validation of coding}

Coding was done by only one researcher due to resource constraints and volume of
source material. As recommended by Kitchenham \cite{Kitchenham2007} we conducted
an experiment with the goal to assess the consistency of coding that two
independent researchers may achieve.
In the experiment Dikert and Paasivaara coded independently a sample of five
primary documents. The sample was hand picked as a representative subset of the
source material. The coding was done relying solely on the guidelines presented
in the previous chapter, and the researchers were careful not to discuss the
choice of codes or interpretations relating to codes before the experiment was
completed. Finally the independent codings of the two researchers were analyzed
with two metrics: by the number of matching themes found, and by the amount of
overlap in quotations similar codes have.
% See Kitcenham, chapter 6.4
